Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-10-28 Article/ici_submm_cloudcorr.tex
restructured manuscript, WORK in PROGRESS

\newcommand{\todo}[1]{{\color{red} #1}}
\newcommand{\ynfcs}{y_\text{NFCS}}
\newcommand{\y}{\vec{y}}

@@

\title{Cloud correction and filtering of operational microwave humidity
  radiances with case specific uncertainty estimation}

@@

This study presents a cloud filtering and correction method for microwave humidity radiances. The method is based on the postulation that sub-millimeter(sub-mm) frequencies can provide a basis for cloud filtering/correction of data measured around 183\,GHz. A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. QRNNs are trained to correct the cloud impact for each 183\,GHz channel using measurements from the target channel and available sub-mm channels. The approach is demonstrated by application to Ice Cloud Imager(ICI) and MicroWave Imager (MWI). As a special case, applicability to smaller satellite missions like Arctic Weather Satellite (AWS), with fewer sub-mm channels, is also evaluated. The performance of QRNN based cloud filtering is also investigated. The results are compared against the NFCS simulations.

Pure-filtering approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are drawn out, cases with low cloud impact are falsely classified as cloudy. This shortcoming is unacceptable in retrieval and assimilation applications and reinforces the necessity for cloud correction. The results from cloud correction show that QRNN is successful in alleviating the cloud contamination to a large extent. Few cases with residual cloud impact deteriorate the performance but filtering out such cases results in error distributions which are symmetric and have low bias and standard deviation. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.  The results show that QRNN is successful in representing the uncertainty for most of scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.

The results show that it can be highly recommended to use all available sub-mm frequencies to estimate the NFCS values of radiances/brightness temperatures. The strategy works well even when only one of the higher frequencies is available. This study uses simulated data, but we can expect to obtain similar performance when data from the new sensors will be available.

@@

\section{Data and methods}
%
\subsection{Satellite Instruments}
\subsubsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels relevant to this study.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		\\
		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		\\
		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		\\
		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		\\
		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		\\
		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		\\
		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		\\
		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		\\
		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		\\
		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\
		I11H&	664.00$\pm$4.20    & \phantom{0}500 & 1.6 		\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	n\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		\\
		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		\\
		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		\\
		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		\\
		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		\\	
		\bottomhline
	\end{tabular}

	\belowtable{} % Table Footnotes
\end{table*}

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models. ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization. While other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels requires remapping to a common footprint \citep{eriksson:towar:20}.

For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}). For brevity, we assumed that all simulations were mapped to a common footprint.

\subsubsection{MicroWave Imager}
%
\label{mwi_channels}
In addition to ICI, the Metop-SG will also have Microwave Imager(MWI) on board. MWI is a conically scanning radiometer and will measure frequencies from 18 GHz up to 183\,GHz \todo{add ref}. All channels up to 89 GHz will receive both horizontal and vertical polarisation, while other frequencies will receive only vertical polarisation. A short summary of the MWI channels used in the study is provided in Table~\ref{tab:ICI_MWI_channels}. MWI also has three  183\,GHz frequencies in common with ICI. The overlapping frequencies shall allow cross-calibration between the two instruments, and provide microwave measurements from 18\,GHz to 664\,GHz on a common scale. The main objective of MWI is to provide data continuity to the existing microwave imager measurements for cloud and precipitation and support regional and global NWP models.

For this study, forward simulations at frequencies around 183.31\,GHz were performed. When ICI and MWI simulations were used together, MWI channels were assumed to be mapped to ICI footprint and resolution. Remapping reduces the noise in MWI from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.

@@

\subsubsection{Cloud Profiling Radar}
%
Cloud Profiling Radar(CPR) is the main instrument on sun-synchronous polar orbit satellite CloudSat (Cloud Satellite) \citep{Stephens2002cloudsat}. It was launched in 2006 and is part of the A-train constellation of four earth observation satellites. CPR is a nadir looking radar operating at 94.05\,GHz and measures the cloud backscatter as a function of distance from the radar, to provide vertical profiles of clouds and precipitation.

In this study, CloudSat profiles were used only to perform the forward simulations for ICI, MWI and AWS.

\subsection{Simulations}
\label{sec:arts_simulations}
%
\subsubsection{Input data}
%
Cloudsat profiles during August 2015 were randomly selected for forward simulations. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land. 
\subsubsection{Simulation setup}
%
**** Some parts copied directly from AWS report *****

\subsubsection{Produced dataset}
%
Using the simulation setup described in previous section,  
220\,000 cases for each ICI and MWI frequency were simulated. For both instruments, the channel frequencies were simulated directly. For AWS, 140\,000 cases were simulated. Forward simulations were performed for 21 monochromatic frequencies. These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.

ARTS simulations are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:ICI_MWI_channels},Table~\ref{tab:specifications_AWS}). For cases where MWI and ICI simulations were assumed to be remapped to a common footprint, the NE$\Delta$T for corresponding to ICI channels was used (See Sect.~\ref{mwi_channels}).

The noise free simulations were divided into training and testing datasets. Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set. The rest were used for testing. A smaller database was selected for AWS. 120\,000 simulations were used for training and the remaining were used for testing.

\subsection{Quantile regression neural networks}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature $\ynfcs$ at a given $187\unit{GHz}$ channel from a vector of
cloud-contaminated observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

@@

%Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel. The three cases have a similar median value but very different spread of the remaining quantiles. These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.

\subsubsection{ QRNN model configurations}
%
\label{QRNN_models}

\begin{table*}[t]
	\caption{Summary of the different QRNN models used in the study.}
	\label{tab:QRNN_models}
	\begin{tabular}{lllll}
		\tophline
		QRNN model & Instrument & Target & Input 183\,GHz channel(s) &Other training inputs \\
		\middlehline
		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{2-5}
		&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
		\cline{2-5}
		& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
		&		& AWS-34/		 &	AWS-34/		   & \\
		&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
		\cline{1-5}
		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{1-5}
		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
		&			& MWI-16/		 &  MWI-16, & \\
		&			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

In the study, three different QRNN cloud-correction models are formulated. The basic construction of all three models is to train for one of the available 183\,GHz channels, using certain input channels. The selection of input channels is categorized by the type of QRNN model chosen.

In the first model, ``QRNN-single'', the training inputs always contain data from the target 183\,GHz channel, and one or more available sub-mm channels. Other 183\,GHz channels are not included in the training. For ICI and MWI, 325\,GHz, 448\,GHz and 664\,GHz are used in the training, while for AWS only 325\,GHz is used.

The second model, ``QRNN-all'', is defined to investigate the  impact of using all 183\,GHz channels concurrently. In this model, the training set includes data from all available 183\,GHz channels, along with other sub-mm channels. This model is applied only to ICI.

The third model, ``QRNN-mwi'' is used only for MWI channels. In this case, all 183\,GHz channels are used concurrently in the training set. No other data from sub-mm channels is used.

For each model, multiple configurations are defined according to the satellite instrument. A summary of the three QRNN models and their different configurations used in this study is provided in Table~\ref{tab:QRNN_models}.

\subsubsection{QRNN implementation}
\label{sec:qrnn-implementation}

The implementation of QRNN is based on PyTorch, an open source machine learning
library \citep{paszke2017automatic}. It is developed and available as a part of
\textit{typhon:tools for atmospheric research} software package
       [\todo{developer's version??}].

For this study, we initialize the quantile loss function with quantile fractions $\tau$ = [0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998] to train the neural network to predict the corresponding quantiles $x_{\tau}$ = [$-3\sigma, -2\sigma, -1\sigma, median, 1\sigma, 2\sigma, 3\sigma $]. QRNN is trained with simulated brightness temperatures from different channels, no other data is included. The input channels are variable and are determined by the type of QRNN model used. The different QRNN models are described in Sect.~\ref{QRNN_models}.

A custom data augmentation scheme is implemented to build a robust learning network. At each training iteration, noise is added to the noise-free inputs according to the measurement uncertainty. The target training data is always kept noise free. This ensures that the model is exposed to different datasets during the entire training process, and avoids memorisation of training samples. The input data is normalized with mean and standard deviation. While training, 10\% of the training data is used for validation.

The neural network is trained with an adaptive form of stochastic batch gradient descent. During the training process, at each iteration, the loss in the validation dataset in monitored. If the validation loss remains stagnant for a certain number of epochs, the training rate is reduced  by a given reduction factor. This process is continued till a minimum learning rate is achieved.

A high performing QRNN model also requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. We use quantile loss and CRPS for evaluation of the model performance.

\section{Results}
%
In this section, QRNN is used to predict the NFCS values for operational humidity channels. The main aim of this study is to demonstrate that sub-mm channels can be used to formulate the cloud filtering/correction of data measured around 183\,GHz. Different combinations of 183\,GHz channels and sub-mm channels are applied to QRNN and the results are compared. The impact of different hyper-parameters on QRNN performance is also discussed. NFCS simulations are used to analyse the prediction accuracy. Results from both pure-filtering and correction are described. Furthermore, the case specific uncertainties obtained from QRNN are also discussed.

\subsection{QRNN network structure}
%
\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-single applied to I2V.}
	\label{fig:grid_search}	
\end{figure*}
In this study, we investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The optimization of other hyper-parameters was not performed and were chosen empirically. Firstly, we performed a grid search to define the structure of the neural network. We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512]. The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}). Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer is selected. For optimising the training parameters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times. Each time with a new initial learning rate. For each training, if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. 
In order to select the batch size, we simply compared the performance for two batch sizes: 128 and 256, and the former gave better results. Concerning number of epochs, we obtained best results when the network was trained longer. Choosing a lower value of epochs (e.g. 50), did not affect the accuracy of the median value, yet deteriorated the prediction uncertainty. We did not optimise the type of activation function and Rectified Linear Unit (ReLu) was used in all layers.

\subsection{ICI}
\subsubsection{Example results}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Predicted quantiles of the conditional distribution of $\ynfcs$ for
		the ICI I1V channel.}
	\label{fig:posterior_distribution_I1V}	
\end{figure}
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
	\label{fig:PDF_predictions}	
\end{figure*}

>>>>

\newcommand{\todo}[1]{{\color{red} #1}}
\newcommand{\ynfcs}{y_\text{NFCS}}
\newcommand{\yonfcs}{y^{o}_\text{NFCS}}
\newcommand{\ynfcsi}{y_\text{NFCS, i}}
\newcommand{\yonfcsi}{y^{o}_\text{NFCS, i}}
\newcommand{\y}{\vec{y}}

@@

%\title{Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation}

\title{Estimation of cloud-corrected microwave humidity radiances with associated uncertainties}

%\title{Cloud correction and uncertainty characterisation of operational microwave humidty channels}

@@

In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances. A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to current sensor MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected. This is comparable to the level of accuracy achieved with operational cloud-filtering techniques. However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact. The resulting error distributions are symmetric with very low spread. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise. The methodology also works well even when only one of the higher frequencies is available. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for most of the scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.

@@

\section{Data and methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems. It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder). As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}. The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

For this study, MWHS-2 simulations were sourced from ECMWF assimilation system. \todo{details?}

\subsubsection{Ice Cloud Imager}
%
%t
\begin{table}[t]	
	\caption{Specifications of ICI channels relevant to this study.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		\\
		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		\\
		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		\\
		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		\\
		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		\\
		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		\\
		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		\\
		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		\\
		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		\\
		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\		
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz.  ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization. While other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels requires remapping to a common footprint \citep{eriksson:towar:20}.

For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}). For brevity, we assume that all simulations are mapped to a common footprint.

@@

\subsection{Simulations}
%
MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF assimilation system. RTTOV and RTTOV-SCATT are used to calculate the radiances in the clear-sky and all-sky conditions respectively. For this study, MWHS-2 brightness temperatures for the period June-July 2020 were used. Out of all the available observations, we extracted data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$. With this filter we had 340\,000 cases for each frequency.

ICI, AWS frequencies were simulated with ARTS. Cloudsat profiles during August 2015 were randomly selected for forward simulations. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface was below 500\,m. Both clear-sky and all-sky scenarios were simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases were simulated. For both instruments, the channel frequencies were simulated directly. For AWS, 140\,000 cases were simulated. Forward simulations were performed for 21 monochromatic frequencies. These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.

All simulations were noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The noise free simulations were split into training and testing datasets. The training dataset was used to train the machine learning model, while the testing dataset was used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations were randomly selected as training dataset, while 70\,000 were used for testing. For ICI, 175\,000 cases were randomly picked to form the training set. The remaining 45\,000 were used for testing. A smaller database was selected for AWS. 120\,000 simulations were used for training and the rest were used for testing.

\subsection{Quantile regression neural networks}
\label{sec:QRNN}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperature $\ynfcs$ at a given $183\unit{GHz}$ channel from a vector of
cloud-contaminated observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

@@

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Kera python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyperparameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to train for each of the available 183\,GHz channels individually, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The selection of input channels is sensor dependent and is described in detail when introduced. The output in both configurations is NFCS value for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

\begin{enumerate}
	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels along with additional data, if relevant. No other 183\,GHz channel is included.

	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input. Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account, but the main difference is the concurrent utilisation of all 183\,GHz frequencies.      
\end{enumerate}

For all three sensors described in this study, one or both of the above QRNN configurations are used.

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{An example showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the selected quantiles. This is contrast with other conventional correction/filtering methods. In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}. This examples illustrate the predicted quantiles for three different cases. For most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviations of point estimates from the corresponding true value ($\yonfcs$) are evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments.

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the true probability distribution. A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN prediction, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we use both calibration plot and predicted errors to assess the correctness of predicted uncertainties.

All evaluation results described in the study have been made on the testing data.

\section{Correcting cloud affected data in MWHS-2}
%
In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel. In order to test the correction approach multiple QRNN experiments are performed and the results are compared for MWHS-2 channel 14. Later the methodology is expanded to other channels.  Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

\subsection{Experiments}
%
For MWHS-2, multiple experiments using both QRNN configurations are performed. The aim of the experiments is to delve into the sensitivity of the cloud correction to different input channels:

\begin{enumerate}

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2. To investigate the potential impact of window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances. In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

	\item In the second experiment, we explore if few of low peaking channels of 118\,GHz could have any potential advantage in cloud correction. To explore their impact, QRNN-single is trained with data from target 183\,GHz, 89\,GHz, 150\,GHz, 118.75$\pm$1.1\,GHz (channel 6), 118.75$\pm$2.5\,GHz (channel 7) and land/sea mask. This combination is denoted as 89+150+118\,GHz

	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction. In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.

	\item The fourth experiment is based on the configuration QRNN-all. In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN. This experiment is motivated by the fact that in all-sky conditions, brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering\cite{buehler:aclou:07}. With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance by providing auxiliary information. It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately. Land/sea mask is also included in the training. This combination is denoted as 89+150+183\,GHz
\end{enumerate}

\subsection{Prediction accuracy}
